---
title: "TITLE"
author: "Ella Kaye"
date: "DATE"
output:
  xaringan::moon_reader:
    includes:
      in_header: header.html
    seal: false
    css: [xaringan-themer.css, extra.css]
    lib_dir: libs
    nature:
      highlightStyle: solarized-light
      highlightLines: true
      countIncrementalSlides: false
---
<!-- To get a footer -->
<!-- layout: true -->
<!-- <div class="my-footer"><span>bit.ly/LINK • @ellamkaye</span></div>  -->

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(collapse = TRUE, fig.retina = 3)
```

```{r meta, echo=FALSE}
library(metathis)
meta() %>%
  meta_general(
    description = "FILL_IN",
    generator = "xaringan and remark.js"
  ) %>% 
  meta_name("github-repo" = "ellakaye/FILL_IN") %>% 
  meta_social(
    title = "FILL_IN",
    url = "FILL_IN",
    image = "https://ellakaye.rbind.io/talk/TALK_NAME/cover-slide.png",
    image_alt = paste(
      "Title slide of PRESENTATION NAME", 
      "Presented at EVENT on DATE by Ella Kaye"
    ),
    og_type = "website",
    og_author = "Ella Kaye",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@ellamkaye"
  )
```

```{r xariganExtra, echo = FALSE, waring = FALSE}
library(xaringanExtra)
use_xaringan_extra(c("tile_view", "clipboard", "extra_css"))
```

---

class: inverse, left, middle

# TITLE

.larger[Ella Kaye | EVENT | DATE]

---

# Me and R

- Studying for a PhD in Statistics at the University of Warwick

- Getting into R:

  - 2014: first R course as part of Statistics MSc 
  - 2015: first taste of `ggplot2` 
  - 2016: first R package 
  - 2017: first community involvement (useR!2017, [Oxford R User Group](https://r-oxford.github.io), [rainbowR](https://rainbowr.slack.com), [@R_LGBTQ](https://twitter.com/R_LGBTQ))
  - 2020: first [TidyTuesday](https://github.com/rfordatascience/tidytuesday) contribution
  - 2021: first ...
  
---

# Overview


---

class: center, middle, inverse

# SECTION 1 

---

# Some slides...

---

class: inverse, center, middle

# RESOURCES

---

# Resources: Slides

- Slides made with [xaringan](https://github.com/yihui/xaringan)

- Slides styled with [xaringanthemer](https://github.com/gadenbuie/xaringanthemer)

- Fonts from [Google Fonts](https://fonts.google.com):
  - Header font in **Cabin**
  - Body text font is **Montserrat**
  - Code font is **Fira Code**
  
- Template available: [ellakaye/emk-talks](https://github.com/EllaKaye/emk-talks)

---

class: inverse, middle

.large[
- TAKE

- HOME

- MESSAGES
]

---

class: left, end

.right[# Thank you!
## Any questions?
### <span style="color:#FDFCFA">Get in touch!</span>]

.large[
`r icon::fa('link')` [bit.ly/LINK]()

`r icon::fa_paper_plane()` [E.Kaye.1@warwick.ac.uk](mailto:E.Kaye.1@warwick.ac.uk)

`r icon::fa_twitter()` [@ellamkaye](https://twitter.com/ellamkaye)

`r icon::fa_laptop()` [ellakaye.rbind.io](https://ellakaye.rbind.io)

`r icon::fa_github()` [github.com/EllaKaye](https://github.com/ellakaye)
]
